Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-03-04 manuscript/manuscript.Rmd
Computed optimised parameters for data where outliers appear on the right-hand (positive) side of the distribution.

```{r optimised_weighting_function_parameters, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Robustness of power transformations after optimising weighting function parameters. ",
  "The distribution of errors, i.e. the difference between robustly fitted $\\hat{\\lambda}^r$ ",
  "and expected $\\hat{\\lambda}_{0}$ found in the absence of outliers, is shown for 1000 randomly ",
  "parametrised asymmetric generalised normal distributions with up to 10% outliers on either side ",
  "of the distribution. The top and bottom panel show errors for the shift-sensitive Box-Cox transformation, ",
  "and shift-sensitive Yeo-Johnson transformation, respectively. ",
  "In each panel, the error distribution for the non-robust transformation is shown to the left ",
  "for comparison with different weighting functions. ",
  "Note that a square root transformation was used along the $y$-axis. Median errors are shown above each distribution."
)

@@

@@

>>>>

```{r optimised_weighting_function_parameters, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Robustness of power transformations after optimising weighting function parameters. ",
  "The distribution of errors, i.e. the difference between robustly fitted $\\hat{\\lambda}^r$ ",
  "and expected $\\hat{\\lambda}_{0}$ found in the absence of outliers, is shown for 1000 randomly ",
  "parametrised asymmetric generalised normal distributions with up to 10% outliers on either side ",
  "of the distribution. The top and bottom panel show errors for the shift-sensitive Box-Cox transformation, ",
  "and shift-sensitive Yeo-Johnson transformation, respectively. ",
  "In each panel, the error distribution for the non-robust transformation is shown to the left ",
  "for comparison with different weighting methods. ",
  "Note that a square root transformation was used along the $y$-axis. Median errors are shown above each distribution."
)

@@

```
# Appendix C: Right-sided outliers

@@

.get_optimised_weighting_function_parameters(manuscript_dir = manuscript_dir, side = "right")
